func-descr.template

### 2025-10-16 reports/capstone-movielens.site/05.appendix.Rmd
Functions described: print_start_date, put_start_date, print_end_date.

>>>>

#### [print_start_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L11) Function {#func.print_start_date}
\

Prints the system date and time at the time the function is called and returns the system's idea of the current date and time.

::: { #func.print_start_date.Usage .sidebar }
##### Usage
\

```{r eval=FALSE}
print_start_date()
```
:::

::: { #func.print_start_date.details .sidebar }
##### Details
\

This function internally calls [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print), [base::date](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/date), and [base::Sys.time](https://www.rdocumentation.org/link/Sys.time?package=base&version=3.6.2) `R` functions.

It first prints the value returned by the `date` function, then returns the object returned by the `Sys.time` function.
:::

::: { #func.print_start_date.value .sidebar }
##### Value
\

Returns an object of class `POSIXct` (see {DateTimeClasses}(https://www.rdocumentation.org/link/DateTimeClasses?package=base&version=3.6.2)).

::: { #func.print_start_date.code .sidebar }
##### Source Code
\

The source code of the [print_start_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L11) function is shown below:
```{r eval=FALSE}
print_start_date <- function(){
  print(date())
  Sys.time()
}
```

::: {.noteblock data-latex=""}
The source code of the [print_start_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L11) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L11) script on _GitHub_.
:::
:::

#### [put_start_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L15) Function {#func.put_start_date}
\

Prints the system date and time to the currently opened log (using the [open_logfile](#func.open_logfile) function described above) at the time the function is called and returns the system's idea of the current date and time.

::: { #func.put_start_date.Usage .sidebar }
##### Usage
\

```{r eval=FALSE}
put_start_date()
```
:::

::: { #func.put_start_date.details .sidebar }
##### Details
\

This function internally calls [logr::put](https://www.rdocumentation.org/packages/logr/versions/1.3.4/topics/log_print), [base::date](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/date), and [base::Sys.time](https://www.rdocumentation.org/link/Sys.time?package=base&version=3.6.2) `R` functions.

It first prints the value returned by the `date` function to the currently opened log, then returns the object returned by the `Sys.time` function.
:::

::: { #func.put_start_date.value .sidebar }
##### Value
\

Returns an object of class `POSIXct` (see {DateTimeClasses}(https://www.rdocumentation.org/link/DateTimeClasses?package=base&version=3.6.2)).

::: { #func.put_start_date.code .sidebar }
##### Source Code
\

The source code of the [put_start_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L15) function is shown below:
```{r eval=FALSE}
put_start_date <- function(){
  print(date())
  Sys.time()
}
```

::: {.noteblock data-latex=""}
The source code of the [put_start_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L15) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L15) script on _GitHub_.
:::
:::

#### [print_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) Function {#func.print_end_date}
\

Prints the system date and time at the time the function is called, and then the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument.

::: { #func.print_end_date.Usage .sidebar }
##### Usage
\

```{r eval=FALSE}
print_end_date(start)
```
:::

::: { #func.print_end_date.args .sidebar }
##### Arguments
\

::: { #func.print_end_date.args.start .sidebar }
  - **start:** An object of class `POSIXct` representing the value of the moment from which time is measured.

::: { #func.print_end_date.details .sidebar }
##### Details
\

This function internally calls [base::print](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/print), [base::date](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/date), and [base::Sys.time](https://www.rdocumentation.org/link/Sys.time?package=base&version=3.6.2) `R` functions.

It first prints the value returned by the `date` function, then returns an object of class `difftime` representing the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument.
:::

::: { #func.print_end_date.value .sidebar }
##### Value
\

Returns an object of class `difftime` representing the time elapsed since the date and time specified by the [start](#func.print_end_date.args.start) argument.

::: { #func.print_end_date.code .sidebar }
##### Source Code
\

The source code of the [print_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) function is shown below:
```{r eval=FALSE}
print_end_date <- function(start){
  print(date())
  print(Sys.time() - start)
}
```

::: {.noteblock data-latex=""}
The source code of the [print_end_date](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#L19) script on _GitHub_.
:::
:::

# ------------------------------------------------------------------------------

### 2025-10-16 reports/capstone-movielens.site/work/func-descr.template.Rmd
Functions described: print_start_date, put_start_date, print_end_date.

>>>>

#### [log_func_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#Lx) Function {#func.log_func_tmpl}
\

::: { #func.log_func_tmpl.Usage .sidebar }
##### Usage
\

```{r eval=FALSE}

::: { #func.log_func_tmpl.args .sidebar }
##### Arguments
\

::: { #func.log_func_tmpl.args.file_name .sidebar }
  - **file_name:** A name used as a base to generate a unique log file name;

::: { #func.log_func_tmpl.details .sidebar }
##### Details
\

::: { #func.log_func_tmpl.value .sidebar }
##### Value
\

::: { #func.log_func_tmpl.code .sidebar }
##### Source Code
\

The source code of the [log_func_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#Lx) function is shown below:
```{r eval=FALSE}

```

::: {.noteblock data-latex=""}
The source code of the [log_func_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#Lx) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#Lx) script on _GitHub_.
:::
:::
